### 2020-02-25 Article.tex

@@

\begin{definition} 
	Given a set $\Sigma$ and an hypergraph $G$, a $\Sigma$-coloring 
	of $G$ is a partial function $\chi$ from $V(G)$ to $\Sigma$. 
	A $\Sigma$-hypergraph $(G,\chi)$ is an hypergraph $G$ equipped
	with a $\Sigma$-coloring of $G$, $\chi$. When $\chi$ is understood
	or is not relevant we may omit it and write just $G$ instead of $(G,\chi)$.\par
	Given two $\Sigma$-hypergraphs $(G_1,\chi_1)$ and $(G_2,\chi_2)$,
	a $\Sigma$-isomorphism between them is an hypergraph isomorphism 
	$f:V(G_1)\rightarrow V(G_2)$ satisfying that
	that for any $v\in V(G_1)$ 
	either (1) $\chi_1(v)=\chi_2(f(v))$, or (2) both $\chi_1(v)$ and $\chi_2(f(v))$ 
	are undefined.	A $\Sigma$ automorphism of a $\Sigma$-hypergraph $G$ is a 
	$\Sigma$-isomorphism from $G$ to itself.
	 \par
	Let $(H,\chi_1), (G,\chi_2)$ be two $\Sigma$-hypergraphs. Then a copy of $H$ in $G$ is
	a sub-hypergraph $G_2\subset G$ such that 
	$(H,\chi_1) \simeq_\Sigma (G_2,\chi_2|_{_{G_2}})$.	
\end{definition}

\begin{theorem} 
	Let $v_1,\dots, v_k\in \N$ be different vertices and let 
	$\Sigma_1,\dots,\Sigma_k$ be finite sets. For each 
	$i\in [k]$ let $\mathcal{T}_i$ be a finite set of non-superimposable
	rooted $\Sigma_i$-trees. 
	For each $n\in N$ and $i\in [k]$ let $\chi_{n,i}$ be a random 
	$\Sigma_i$ coloring over $G_n$ such that for any $w\in \N$ and any $S \in \Sigma_i$
	the limit
	\[
	\Ln \mathrm{Pr}\big( \chi_n(w)=S\big)
	\]
	exists and does not depend on the chosen $w$. For each 
	$S \in \Sigma_i$, let $\mu_{i,S}$ denote last limit. 
	Given a tree $T\in \mathcal{T}_i$ let
	\[
	\lambda_{i,T}=\frac{1}{|Aut(T)|}\prod_{S\in \Sigma_i} \mu_{i,S}^{v(S,T)} 
	\]	
\end{theorem}

>>>>

\subsection{Counting colored sub-hypergraphs}

\begin{definition} 
	Given a set $\Sigma$ and an hypergraph $G$, a $\Sigma$-coloring 
	of $G$ is a function $\chi: V(G)\rightarrow \Sigma$. 
	A $\Sigma$-hypergraph $(G,\chi)$ is an hypergraph $G$ equipped
	with a $\Sigma$-coloring of $G$, $\chi$. When $\chi$ is understood
	or is not relevant we may omit it and write just $G$ instead of $(G,\chi)$.\par
	Given two $\Sigma$-hypergraphs $(G_1,\chi_1)$ and $(G_2,\chi_2)$,
	a $\Sigma$-isomorphism between them is an hypergraph isomorphism 
	$f:V(G_1)\rightarrow V(G_2)$ satisfying that
	that for any $v\in V(G_1)$, $\chi_1(v)=\chi_2(f(v))$.
	A $\Sigma$ automorphism of a $\Sigma$-hypergraph $G$ is a 
	$\Sigma$-isomorphism from $G$ to itself.
	\par
	Let $(H,\chi_1), (G,\chi_2)$ be two $\Sigma$-hypergraphs. 
	Then a copy of $H$ in $G$ is
	a sub-hypergraph $G_2\subset G$ such that 
	$(H,\chi_1) \simeq_\Sigma (G_2,\chi_2|_{_{G_2}})$.	\par

	Notation: $Copies([n],(G, \chi))$
	Notation: $H\subset_{\Sigma}G$.

\end{definition}

\begin{definition}
	Given a set $\Sigma$, a random $\Sigma$-coloring of $G_n$ is 
	a random function $\chi_n: [n]\rightarrow \Sigma$. We say that	
	$\chi_n$ is symmetric if for any $s\in \Sigma$ the probability
	$\mathrm{Pr}\big( \chi_n(v)=s \big)$ is the same for any vertex
	$v\in [n]$. Notation $\mathrm{Pr}\big[\chi_n=s\big]$. \par
	For each $n\in \N$ let $\chi_n$ be a random $\Sigma$-coloring of $G_n$.
	We say that the succession $(\chi_n)_{n\in \N}$ is regular if
	the $\chi_n$'s are symmetric and for any $s\in \Sigma$ the limit
	$\Ln \mathrm{Pr}\big[ \chi_n = s \big]$ exists. 
\end{definition}

Remark: A random coloring $\chi$ of $G_n$ does not have to be independent from
$G_n$. In fact, in the cases we are going to consider $\chi$ will be determined
by $G_n$.

\begin{definition}
	Let $\Sigma_1,\dots,\Sigma_k$ be a sets. For each $i\in [k]$
	let $(\chi_{n,i})_{n \in \N}$ be a random regular sequence of
	$\Sigma_i$-colorings.
	Let $\mathcal{F}$ be a family of hypergraphs.
	We say that the successions $(\chi_{n,1})_{n \in \N},\dots,
	(\chi_{n,k})_{n \in \N}$ are $\mathcal{F}$-independent if
	for any given
	\begin{itemize}
		\item fixed finite number of copies of hypergraphs from 
		$\mathcal{F}$ in $\N$,
		\[
		S \subset \bigcup_{H\in \mathcal{F}} Copies(H,\N).
		\]		
		\item fixed disjoint sets of vertices 
		$V_1, \dots, V_k \subset \bigcup_{H\in S} V(H).$
		\item for each $i\in [k]$ and each $v\in V_i$, 
		a fixed label $s(v)\in \Sigma_i$
	\end{itemize}
	it is satisfied
	\[
	\Ln \mathrm{Pr}\big(
	\bigwedge_{i=1}^k \bigwedge_{v\in V_i} \chi_{n,i}(v)=s(v)
	\, \big| \, \bigwedge_{H\in S} H\subset G_n \,
	\big) = \prod_{i=1}^k \prod_{v\in V_i} \mathrm{Pr}\big[\chi_i=s(v)
	\big]		
	\]  
\end{definition}

\begin{definition}
	Let $H_1,\dots, H_k$ be hypergraphs. Let $n,b_1,\dots,b_k\in \N$
	A $b_1,\dots,b_k$-configuration of $H_1,\dots, H_k$ over $[n]$
	is an ordered tuple $(O_1,\dots,O_k)$ where for each $i\in [k]$
	$O_i$ is an ordered $b_i$-tuple of different $H_i$-hypergraphs 
	over $[n]$. In other words, each $O_i$ is an element of
	$\big( Copies(H,[n])\big)_{b_i}$, and the set of 
	$b_1,\dots,b_k$-configurations of $H_1,\dots, H_k$ over $[n]$
	is precisely $\prod_{i=1}^{k}\big( Copies(H,[n])\big)_{b_i}$.
\end{definition}

\begin{definition}
 	The underlying set of a configuration $\omega
 	=  (O_1, \dots, O_k)$ is the defined as
 	$S_{\omega}:=\{ H\in O_i \, | \, i\in [k]\}$.
 	A configuration $\omega$ is called disjoint
	if all the hypergraphs belonging to its underlying set
	$S_\omega$ have disjoint sets of vertices. 
\end{definition}

\begin{theorem}
	Let $k\in \N$. For each $i\in [k]$ 
	\begin{itemize}
		\item Let $\Sigma_i$ be a set, let $H_i$ be a unicycle and 
		let $\rho^i$ be a $\Sigma_i$-coloring of $H_i$.
		\item Let $(\chi^i_n)_{n\in\N}$ be a succession of
		random $\Sigma_i$-colorings of $(G_n)_{n\in \N}$
		\item Let $X_{i,n}$ be the random variable that counts
		the number of copies of $(H_i, \rho^i)$ in
		$(G_n,\chi^i_n)$.				
	\end{itemize}
	Let $\mathcal{F}=\{H_1,\dots, H_n\}$. Suppose that the
	successions $(\chi^1_n)_{n\in\N}, \dots, (\chi^k_n)_{n\in\N}$
	are $\mathcal{F}$-independent. Then, for each $a_1,\dots,a_k\in \N$
	\[
	\Ln \mathrm{Pr}\big( \bigwedge_{i=1}^k X_{n,i}=a_i  \big)=
	\prod_{i=1}^{k}e^{-\lambda_i}\frac{\lambda_i^{a_i}}{a_i!},
	\]
	where for each $i\in [k]$,
	\[
	\lambda_i:= \frac{\prod_{j\in \sigma} \beta_j^{e_j(H_i)}}{|Aut(H_i,\rho^i)|} 
	\prod_{v\in V(H_i)} \mathrm{Pr}\big[\chi^i=\rho^i(v)\big].
	\]
\end{theorem}
\begin{proof}
	Because of \cref{thm:BrunSieve} we only need to show that for any 
	fixed $b_1,\dots, b_k\in \N$ it is satisfied
	\[
	\Ln \mathrm{E}\big[ \prod_{i=1}^{k} (X_{n,i})_{b_i} \big]=
	\prod_{i=1}^{k} \lambda_i^{b_i}.		
	\]
	For each $n\in \N$ let $\Omega_n$ be the set
	of $b_1, \dots, b_k$-configurations of $(H_1,\rho^1)
	,\dots, (H_k, \rho^k)$ over $[n]$. Then
	\[
	\Ln \mathrm{E}\big[ \prod_{i=1}^{k} (X_{n,i})_{b_i} \big]=
	\Ln \sum_{(O_1,\dots, O_k)\in \Omega_n}
	\mathrm{Pr}
	\big(
	(O_1,\dots, O_k) \subset G_n
	\big).	
	\]
	Let $\Omega^{\times}_n\subset \Omega_n$ be the set of 
	disjoint configurations in $\Omega_n$. Because of REF,
	\[
	\Ln \sum_{(O_1,\dots, O_k)\in \Omega_n}
	\mathrm{Pr}
	\big(
	(O_1,\dots, O_k) \subset G_n
	\big)=
	\Ln \sum_{(O_1,\dots, O_k)\in \Omega^\times_n}
	\mathrm{Pr}\big(
	(O_1,\dots, O_k) \subset G_n
	\big).
	\]
	Because of the symmetry of the random hypergraph $G_n$ and
	the colorings $\chi^1_n, \dots, \chi^k_n$ the probability
	$\mathrm{Pr}\big(
	(O_1,\dots, O_k) \subset G_n
	\big)$ is the same for all $(U_1,\dots, U_k)\in 
	\Omega^\times_n$. Thus, if we fix
	$(O_1, \dots, O_k)$ a 
	disjoint $b_1,\dots,b_k$-configuration of
	 $(H_1,\rho^1)
	,\dots, (H_k, \rho^k)$ over $\N$, 
	\[
	\Ln \sum_{(O_1,\dots, O_k)\in \Omega^\times_n}
	\mathrm{Pr}\big(
	(O_1,\dots, O_k) \subset G_n
	\big) =
	\Ln |\Omega^{\times}_n|	\mathrm{Pr}\big(
	(U_1,\dots, U_k) \subset G_n
	\big).
	\]

\end{proof}

@@
